---
title: "Activity 3 - MLR"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r eval = FALSE, echo = FALSE}
autos <- read_csv("Automobile.csv")

```
Is this an observational study or an experiment?
I believe this is from an oobservational study


You will need to create appropriate univariate graphs to help in answering this:

Describe the distribution of your response variable. Is the distribution skewed? Are there any other interesting/odd features (outliers, multiple peaks, etc.)? What does that tell you about countries’ personal freedoms? Is this what you expected to see? Why, or why not?
```{r}
ggplot(autos, aes(x = mpg)) +
  geom_histogram(fill = "lightblue", color = "black", bins = 30) +
  labs(x = "mpg", y = "Frequency", title = "Distribution of mpg in Autos dataset")
```




Excluding your response variable, select two other numeric variables (hint: look for <dbl> or <int> designations) and describe their relationship with each other using an appropriate visualization.

```{r}
ggplot(autos, aes(x = weight, y = horsepower)) +
  geom_point(color = "#2E8B57", size = 3, alpha = 0.7) +
  labs(x = "Weight", y = "Horsepower", title = "Scatter Plot of Weight vs. Horsepower") +
  theme_minimal() +
  theme(
    plot.background = element_rect(fill = "lightgray"),
    panel.grid.major = element_line(color = "white"),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black"),
    axis.text = element_text(color = "black"),
    axis.title = element_text(color = "black", size = 12, face = "bold"),
    plot.title = element_text(size = 14, face = "bold")
  )

```
```{r}
autos %>% 
  select(mpg, weight, horsepower) %>% 
  ggpairs()
```

